---
title: "lab5"
author: "Margaret Hammond"
date: "10/25/2021"
output: 
  html_document: 
    toc: yes
    theme: united
    code_folding: hide
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section we'll use the `t.test()` function to calculate confidence intervals. 

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too.

```{r}
## Mock sample
otter_lengths <- c(12, 3.9, 5, 80, 2, 57, 10, 9)

# Find the confidence interval of the sample
otter_ci <- t.test(otter_lengths)

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```

CI: if we took multiple samples of this population, we expect 95% of these samples to hold the true population mean.

Mean otter length is 22.363 inches $\pm$ 29.320 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [-2.149, 46.874] inches.

#### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches. That in line code will update to any data changes. Woo!

