---
title: "lab5"
author: "Margaret Hammond"
date: "10/25/2021"
output: 
  html_document: 
    toc: yes
    theme: united
    code_folding: hide
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section we'll use the `t.test()` function to calculate confidence intervals. 

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too.

```{r}
## Mock sample
otter_lengths <- c(12, 3.9, 5, 80, 2, 57, 10, 9)

# Find the confidence interval of the sample
otter_ci <- t.test(otter_lengths)

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```

CI: if we took multiple samples of this population, we expect 95% of these samples to hold the true population mean.

Mean otter length is 22.363 inches $\pm$ 29.320 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [-2.149, 46.874] inches.

#### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1)`, `r round(otter_ci$conf.int[2], 1)`] inches.

If you are trying to inline code by the value is a vector, use [#] to get just one value.

## Part 2: Two-sample t-tests

### Example 1

Make two mock samples, ask ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?

```{r}
# Make my mock samples
oak_trees <- c(21, 20, 32, 25, 12, 39, 20, 24)
  
  
pine_trees <-c(35, 39, 41, 29, 18, 28, 46, 27)

# Two-sample t-test
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same
# ie.: trees are drawn from populations with the same mean height

```

if these samples are taken from populations with the same mean height, then there is A 6% chance of taking a random sample from each population and finding that the sample means are at least as different as we found (by random chance). We accept the null hypothesis because it is above 5%. 

The mean heights of oak and pine trees were (X +- Y) and (X +- Y), respectively, and the difference was not significant (t(`r trees_t$parameter`) = `r trees_t$statistic`, p = `r trees_t$p.value`).

"t(df) = t-statistic, p = p-value"
**AVOID**: p = 0. That will never happen.

When things get really small (usually p < 0.001)
**Not great**: p = 0.00000000000012
**Better**: p < 0.001

## Part 3: Another t-test with cars data

Using the `mpg` dataset

### Take a look at the data

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))

# Check remaining levels using unique
unique(compact_suv$class)
```

Creat a histogram of city gas mileage (cty) faceted by class starting from compact_suv.

```{r}
ggplot(data = compact_suv, aes(x = cty)) +
  geom_histogram(bins = 12) + 
  facet_wrap(~ class)

ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~ class)
```

Find some summary statistic for each group

```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city = mean(cty),
    sd_city = sd(cty),
    sample_size = n()
  )
car_stats
```

The t.test() function REALLY wants vectors of things. Use the `pull()` function to pull out a vector from a data frame.

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)
```

H0:Mean city gas mileages from SUVs and copany cars are the same; 

```{r}
t.test(compact_sample, suv_sample)
```
WE REJECT THE NULL HYPOT. There is a significant difference in mean city mpg for compact vs suv cars. 
